Supporting Information

### 2018-04-03 SupportingInformation.Rmd
changes to deal with a warning when we try to fit a BB7 to negatively correlated data

<!--The message=F and warning=F flags are to suppress warnings that come when you pass a parameter
of 0 to the Frank or Clayton copulas. These are technicallly boundary cases for these families.
They correspond to the independent copula. The packages we use provide the indepdent copula, but
issue a warning. Since anyway we want the independent copula, we can suppress the warning. We ran this
without the warning and it is OK to supress it.-->
<!-- The lines you are talking about appeared as message not as warning(actualy no warning appered for this chunk), so we have to set message=F here-->
```{r stat_testing_save_and_plot_result, message=F, echo=F, cache=T, cache.extra=list(seed,mtime("TestStats_multivar_dataset.R"),mtime("CopulaFunctions.R"),mtime("CopulaFunctions_flexible.R"))}
source("TestStats_multivar_dataset.R")
set.seed(seed)

>>>>

<!--The message=F and warning=F flags are to suppress warnings that come when you pass a parameter
of 0 to the Frank or Clayton copulas. These are technicallly boundary cases for these families.
They correspond to the independent copula. The packages we use provide the indepdent copula, but
issue a warning. Since anyway we want the independent copula, we can suppress the warning. We ran this
without the warning and it is OK to supress it.-->
<!-- The lines you are talking about appeared as message not as warning(actualy no warning appered for this chunk), so we have to set message=F here-->
```{r stat_testing_save_and_plot_result, message=F, results="hide", echo=F, cache=T, cache.extra=list(seed,mtime("TestStats_multivar_dataset.R"),mtime("CopulaFunctions.R"),mtime("CopulaFunctions_flexible.R"))}
source("TestStats_multivar_dataset.R")
set.seed(seed)
